---
title: "DATA607_Assignment10_Resubmit"
author: "Gabriel Santos"
date: "2022-11-11"
output: html_document
---


### Loading Libraries
```{r}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(stringr)
library(wordcloud)
library(reshape2)
library(tidyr)
library(dplyr)
```

### Sentiment analysis with tidy data
The following section is code from [Chapter 2](https://www.tidytextmining.com/sentiment.html) 

### Dataset
```{r}
get_sentiments("afinn")
```

```{r}
get_sentiments("bing")
```

```{r}
get_sentiments("nrc")
```
### Joining, by = "word"
```{r}
library(stringr)

tidy_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                                                 ignore_case = TRUE)))) %>%
  ungroup() %>%
  unnest_tokens(word, text)

nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_books %>%
  filter(book == "Emma") %>%
  inner_join(nrc_joy) %>%
  count(word, sort = TRUE)
```

```{r}
jane_austen_sentiment <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(book, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

```{r}
library(ggplot2)

ggplot(jane_austen_sentiment, aes(index, sentiment, fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free_x")
```

```{r}
pride_prejudice <- tidy_books %>% 
  filter(book == "Pride & Prejudice")

pride_prejudice
```

```{r}
afinn <- pride_prejudice %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(index = linenumber %/% 80) %>% 
  summarise(sentiment = sum(value)) %>% 
  mutate(method = "AFINN")
```

```{r}
bing_and_nrc <- bind_rows(pride_prejudice %>% 
                            inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing et al."),
                          pride_prejudice %>% 
                            inner_join(get_sentiments("nrc") %>% 
                                         filter(sentiment %in% c("positive", 
                                                                 "negative"))) %>%
                            mutate(method = "NRC")) %>%
  count(method, index = linenumber %/% 80, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

```{r}
bind_rows(afinn, 
          bing_and_nrc) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~method, ncol = 1, scales = "free_y")
```

```{r}
get_sentiments("nrc") %>% 
  filter(sentiment %in% c("positive", 
                          "negative")) %>% 
  count(sentiment)
```

```{r}
get_sentiments("bing") %>% 
  count(sentiment)
```

```{r}
bing_word_counts <- tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()
```

```{r}
bing_word_counts
```

```{r}
bing_word_counts %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()
```

```{r}
custom_stop_words <- bind_rows(tibble(word = c("miss"), 
                                      lexicon = c("custom")), 
                               stop_words)

custom_stop_words
```

```{r}
tidy_books %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

```{r}
tidy_books %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("gray20", "gray80"),
                   max.words = 100)
```

```{r}
PandP_sentences <- tibble(text = prideprejudice) %>% 
  unnest_tokens(sentence, text, token = "sentences")
PandP_sentences$sentence[2]
```

```{r}
austen_chapters <- austen_books() %>%
  group_by(book) %>%
  unnest_tokens(chapter, text, token = "regex", 
                pattern = "Chapter|CHAPTER [\\dIVXLC]") %>%
  ungroup()

austen_chapters %>% 
  group_by(book) %>% 
  summarise(chapters = n())
```

```{r}
bingnegative <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

wordcounts <- tidy_books %>%
  group_by(book, chapter) %>%
  summarize(words = n())

tidy_books %>%
  semi_join(bingnegative) %>%
  group_by(book, chapter) %>%
  summarize(negativewords = n()) %>%
  left_join(wordcounts, by = c("book", "chapter")) %>%
  mutate(ratio = negativewords/words) %>%
  filter(chapter != 0) %>%
  top_n(1) %>%
  ungroup()
```

#### *Second corpus analysis*


```{r}
library(dplyr)
library(janeaustenr)
library(tidytext)
book_words <- austen_books() %>%
  unnest_tokens(word, text) %>%
  count(book, word, sort = TRUE)
total_words <- book_words %>% 
  group_by(book) %>% 
  summarize(total = sum(n))
book_words <- left_join(book_words, total_words)
```

```{r}
book_words
```

```{r}
library(ggplot2)
ggplot(book_words, aes(n/total, fill = book)) +
  geom_histogram(show.legend = FALSE) +
  xlim(NA, 0.0009) +
  facet_wrap(~book, ncol = 2, scales = "free_y")
```

```{r}
freq_by_rank <- book_words %>% 
  group_by(book) %>% 
  mutate(rank = row_number(), 
         `term frequency` = n/total) %>%
  ungroup()

freq_by_rank
```

```{r}
freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```

```{r}
rank_subset <- freq_by_rank %>% 
  filter(rank < 500,
         rank > 10)

lm(log10(`term frequency`) ~ log10(rank), data = rank_subset)
```

```{r}
freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = book)) + 
  geom_abline(intercept = -0.62, slope = -1.1, 
              color = "gray50", linetype = 2) +
  geom_line(size = 1.1, alpha = 0.8, show.legend = FALSE) + 
  scale_x_log10() +
  scale_y_log10()
```

```{r}
book_tf_idf <- book_words %>%
  bind_tf_idf(word, book, n)

book_tf_idf
```

```{r}
book_tf_idf %>%
  select(-total) %>%
  arrange(desc(tf_idf))
```

```{r}
library(forcats)

book_tf_idf %>%
  group_by(book) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = book)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~book, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)
```

```{r}
text <- c("have kept my feelings to myself -",
          "were kindly smiled on by the mother and daughter -",
          "The Carriage held but just Ourselves -",
          "and Immortality")

text
```

```{r}
library(dplyr)
text_df <- tibble(line = 1:4, text = text)

text_df
```

Split the text and transform it into an ordered data structure, through the process of tokenization

```{r}
library(tidytext)
text_df %>%
  unnest_tokens(word, text)
```

```{r}
library(janeaustenr)
library(dplyr)
library(stringr)

original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]",
                                           ignore_case = TRUE)))) %>%
  ungroup()

original_books
```

```{r}
library(tidytext)
tidy_books <- original_books %>%
  unnest_tokens(word, text)

tidy_books
```

```{r}
data(stop_words)

tidy_books <- tidy_books %>%
  anti_join(stop_words)
```

```{r}
tidy_books %>%
  count(word, sort = TRUE) 
```

```{r}
library(ggplot2)

tidy_books %>%
  count(word, sort = TRUE) %>%
  filter(n > 600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col(fill='darkblue') +
  labs(y = NULL)
```

### *Conclusion*

Sentiment analysis allows us to understand the emotional content of a text.Perform a sentiment analysis on the text.Determine the use of positive and negative words by performing a sentiment analysis. The text has more negative than positive sentiments.

Sentiment analysis is based on automated evaluation to determine whether a text has been written with a positive or negative intention. The sentiment analysis can be applied to different environments, for example evaluating a book. In the Marketing area, they can use this method to obtain information that allows them to understand the way in which customers react to a specific product or service.